A parallelised and distributed approach to implementing Conway's Game of Life

### 2022-12-05 report/article_2.tex
finished parallel report

\section{memory sharing}
\subsection{Motivation}
Looking at our achievements in counting, we noticed overhead associated with channel communication.
Exploring \href{https://github.com/golang/go/blob/4fc9565ffce91c4299903f7c17a275f0786734a1/src/runtime/chan.go}
{Go's implementation for channels}, we see much overhead. Since we know a channel is a thread-safe memory sharing
mechanism, we can rid the overhead, using only mutex locks and condition variables.
\subsection{Implementation}
Our homemade channel implementation does the following:
\begin{enumerate}[noitemsep]
  \item Acquire the mutex lock
  \item While \texttt{condition} is false, await broadcast unless non-blocking send
  \item Use the value, then broadcast to other processes
  \item Finally, unlock mutex
\end{enumerate}
We introduce 2 methods, \texttt{Send} \& \texttt{Receive}. \texttt{Send} waits for the memory space 
to be empty, and replaces it with a value. \texttt{Receive} waits for the memory space to point to a value, and then 
replaces it with \texttt{nil}. \texttt{Go 1.12} does not have generics, which vastly complicated implementation. 
Benchmarks with memory sharing (and bitmasked \texttt{getNeighbourCount}) is shown in Fig. 4.
\subsection{On the topic of Analysis 3}
benchmarks go here, analysis here

Lorem ipsum dolor sit amet, consectetur adipiscing elit.
\blindtext % Dummy text

@@

\section{benchmarking and critical analysis of enabling SDL}

% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\begin{itemize}
  \item show graphs and describe shape and differences of with vs without SDL
  \item explain how SDL works
  \item explain how this causes bottlenecks
\end{itemize}
%------------------------------------------------

>>>>

\section{memory sharing}
\subsection{Motivation}
Looking at our achievements in counting, we noticed overhead associated with channel communication.
Exploring \href{https://github.com/golang/go/blob/4fc9565ffce91c4299903f7c17a275f0786734a1/src/runtime/chan.go}
{Go's implementation for channels}, we see much overhead. Since we know a channel is a thread-safe memory sharing
mechanism, we can rid the overhead, using only mutex locks and condition variables.
\subsection{Implementation}
Our homemade channel implementation does the following:
\begin{enumerate}[noitemsep]
  \item Acquire the mutex lock
  \item While \texttt{condition} is false, await broadcast unless non-blocking send
  \item Use the value, then broadcast to other processes
  \item Finally, unlock mutex
\end{enumerate}
\begin{figure}
  \includegraphics[width=\linewidth]{memshare.png}
  \caption{Memory Sharing}
  \label{fig:chart4}
\end{figure}
We introduce 2 methods, \texttt{Send} \& \texttt{Receive}. \texttt{Send} waits for the memory space 
to be empty, and replaces it with a value. \texttt{Receive} waits for the memory space to point to a value, and then 
replaces it with \texttt{nil}. \texttt{Go 1.12} does not have generics, which vastly complicated implementation. 
Benchmarks with memory sharing (and bitmasked \texttt{getNeighbourCount}) is shown in Fig. 4.
\subsection{On the topic of Analysis 3}
This data was not very analysable. The lack of clear trend and sporadic data points suggests no real difference 
in performance when adding memory sharing, or faulty implementation (which we realistically do consider a possibility).
A trend, if any, we identify is that the Modulo performance suffered, but due to the lack of clarity, this is inconclusive.
We add that repeated trials yielded similar style results. Our method used the following: \[\forall t \in T: ORIG[t] - MEM[t]\]
Where $MEM$ is memory sharing implementation time, $ORIG$ is channel impl. time, $T$ is the number of threads.

\section{Distributed Implementation}

@@

\section{benchmarking and critical analysis of enabling SDL}
% i dont think we need benchmarking of SDL
% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\begin{itemize}
  \item show graphs and describe shape and differences of with vs without SDL
  \item explain how SDL works
  \item explain how this causes bottlenecks
\end{itemize}
%------------------------------------------------
